---
title: "Single-celled bottlenecks, germlines and the evolution of complex multi-cellularity"
output:
  html_document:
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_float: yes
    fig_caption: yes
  html_notebook:
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_float: yes
    fig_caption: TRUE
---

This script re-creates the analyses of Fisher et al 2013 using this dataset. As this dataset is built on the data from that study (with the addition of a small number of plants), then the results should be v. similar. 

# Pre-amble
## load packages
```{r packages}
library(ape)
library(ggplot2)
library(tidyverse)
library(knitr)
library(brms) #https://rdrr.io/cran/brms/f/vignettes/brms_phylogenetics.Rmd
library(tidybayes)
library(rotl) #see https://cran.r-project.org/web/packages/rotl/vignettes/rotl.html
```

## read in data
```{r data_input}
df<- read.csv('data/germline_data_1.0.csv') #read in csv
```

## create phylogeny files
```{r phylogeny_creation, message=F, results='hide'}

ResolvedNames <- tnrs_match_names(df$species.updated.rotl, context_name = 'All life') #search for similar names in the 'open tree of life' project (ROTL)
ResolvedNames$IsInTree <- is_in_tree(ResolvedNames$ott_id) #T/F, did the above find a match that can be put in the phylogeny? 
ResolvedNamesInTree<- subset(ResolvedNames, IsInTree==T) #subset to only those where present in the phylogeny

AllTree<- tol_induced_subtree(ResolvedNamesInTree$ott_id, label_format = 'id') #draw the phylogeny

# tree with resolved polytomies:
ResolvedPolytomiesTree<- multi2di(AllTree)

# write to files
write.tree(AllTree, file='data/phylogeny_all.txt') #phylogeny
write.tree(AllTree, file='data/phylogeny_all_res_polytomy.txt') #phylogeny with resolved polytomies
write.csv(ResolvedNames, 'data/phylogeny_species_names.csv') #list of names
write.csv(ResolvedNamesInTree, 'data/phylogeny_species_names_in_tree.csv') #list of names that are present in the tree
```

```{r plot_phylogeny, fig.cap="Simple phylogenetic tree constructed using the Open Tree of Life, needs manually checked for errors"}
#plot phylogeny to check
plot(AllTree, no.margin = TRUE, cex = 0.5, label.offset = 0.5)
```


# Recreating results in Fisher without phylogeny

As practise for analyses of germline data.

## 1. is clonal group formation more likely to produce obligate multi-cellularity?  
### defining the model
Have defined a v. simple, pretty non-informative prior (makes everything run faster). As a default, brms has flat prior, but defining a simple prior makes things run a bit quicker.  
Summary table to eyeball results:
```{r obl_summary}
summary<- df %>%
  group_by(Obligate_or_facultative) %>%
  count()#summary table just to check that the results kinda fit

print(summary)
```

```{r obl_model}
#fit the model 
fit_obl<-
  brm(data = df,
      family=bernoulli(link = 'logit'), # family of model
      formula = Obligate_or_facultative ~ 0 + clonal,  #formula, the 0 means that there are estimates for both clonal and non-clonal, rather than relative to each other
      iter = 600000, warmup = 10000, chains = 5,thin = 100, cores = 5, #chain settings
      prior = prior(normal(0, 10), "b"), #defining the priors- for things in 'class b' set this prior. (can also use get_priors() and set_priors() fucncitons) 
      file = 'fits/obligate' ) 

```

### Assessing model:  
Assessing whether the chains converged, whether the predictions are okay, etc. 
```{r obl_model_assessment}
plot(fit_obl) #check that chains converged
pp_check(fit_obl) #check the predictions
plot(conditional_effects(fit_obl), points = TRUE) #show the effects of the c

summary(fit_obl)
posterior_summary(fit_obl, robust = T) #what are the medians for coefficients? if F, then returns means
```

### Hypothesis testing
Do clonal groups contain more cells than non-clonal?
```{r obl_model_testing}
hyp = hypothesis(fit_obl,  "clonalclonal > clonalnonMclonal") #test hypothesis that clonal is more likely to produce obligate multicellularity
hyp
plot(hyp)
```

This is another way of posting from the brms anaysis book online (https://bookdown.org/content/3686/)
```{r}
post <- posterior_samples(fit_obl) #take the posterior samples
post <- #convert them back to probabilities (from log odds)
  post %>% 
  summarise(theta_clonal = exp(b_clonalclonal) / (1 + exp(b_clonalclonal)),
         theta_nonclonal     = exp(b_clonalnonMclonal)/ (1 + exp(b_clonalnonMclonal))) %>% 
  mutate(`theta_clonal - theta_nonclonal` = theta_clonal - theta_nonclonal)

gathered_post <- # pivot table to make plot 
  post %>% 
  select(starts_with("theta")) %>% 
  gather() %>% 
  mutate(key = factor(key, levels = c("theta_clonal", "theta_nonclonal", "theta_clonal - theta_nonclonal")))

gathered_post %>% #draw plot
  ggplot(aes(x = value, y = 0, fill = key)) +
  stat_histinterval(point_interval = mode_hdi, .width = .95,
                    slab_color = "white", outline_bars = T,
                    normalize = "panels") +
  scale_y_continuous(NULL, breaks = NULL) +
  theme_minimal() +
  facet_wrap(~key, scales = 'free') 
```


## 2. does clonal group formation produce groups with more cells?

```{r}
df %>%
  group_by(clonal) %>%
  summarise(cell_mean = mean(log(cell_number), na.rm = T)) #summary table just to check that the results kinda fit
            
prior <- get_prior(log(cell_number) ~ 0 + clonal, family=gaussian(), data = df) #what priors do we need?
```

```{r}
#fit the model 
fit_num<-
  brm(data = df,
      family=gaussian(),
      formula = log(cell_number) ~ 0 + clonal, 
      iter = 600000, warmup = 100000, chains = 5, thin = 100, cores = 5,
      prior = prior(normal(0, 10), "b"), file = 'fits/cell_number' ) # same simple prior
```

```{r}
plot(fit_num) #check that chains converged
pp_check(fit_num) #check the predictions
summary(fit_num) #summary of model 
posterior_summary(fit_num, robust = T)
plot(conditional_effects(fit_num), points = TRUE) 
```

testing hypothesis: 
```{r}
hyp = hypothesis(fit_num,  "clonalclonal > clonalnonMclonal") #test hypothesis that there is no difference based on coefficients
hyp
plot(hyp)
```

## Result 3: number of cell types
```{r}
df %>%
  group_by(clonal) %>%
  summarise(cell_mean = mean(cell_types, na.rm = T)) #summary table just to check that the results kinda fit

prior <- get_prior(cell_types ~ 0 + clonal + cell_number, family=poisson(), data = df) #defining what priors we need
```
fit the model 
```{r}
fit_type<-
  brm(data = df,
      family=poisson(),
      formula = cell_types ~ 0 + clonal + scale(log(cell_number)),
      iter = 600000, warmup = 100000, chains = 5, thin = 1000, cores = 5,
      prior = prior(normal(0, 10), "b"), file = 'fits/cell_type')
```

```{r}
plot(fit_type) #check that chains converged
pp_check(fit_type) #check the predictions
summary(fit_type) #summary of model 
posterior_summary(fit_type, robust = T)
plot(conditional_effects(fit_type), points = TRUE, ask = F) 
```

```{r}
hyp = hypothesis(fit_type,  "clonalclonal > clonalnonMclonal") #test hypothesis that there is no difference based on coefficients
hyp
plot(hyp)

hyp = hypothesis(fit_type,  "scalelogcell_number = 0") #test hypothesis that there is no difference based on coefficients
hyp
plot(hyp)
```

## complex vs simple

```{r}

#fit the model 
fit_complex<-
  brm(data = df,
      family=bernoulli(link = 'logit'),
      formula = Simple_or_complex ~ 0 + clonal, 
      iter = 600000, warmup = 10000, chains = 5,thin = 100, cores = 5,
      prior = prior(normal(0, 10), "b"), file = 'fits/fit_complex' )

plot(fit_complex) #check that chains converged
pp_check(fit_complex) #check the predictions
plot(conditional_effects(fit_complex), points = TRUE) 

summary(fit_complex)
posterior_summary(fit_complex, robust = T) #what are the medians for coefficients? if F, then returns means

hyp = hypothesis(fit_complex,  "clonalclonal > clonalnonMclonal") #test hypothesis that there is no difference based on coefficients
hyp
plot(hyp)

```


# with phylogeny included

```{r}
#read in phylogeny
phylo<- ape::read.tree('data/phylogeny_all.txt')


#subset df above with just those that are in the tree (note some missing)
names_in_tree<- read.csv('data/phylogeny_species_names_in_tree.csv')
names_in_tree$ott_id<- paste('ott',names_in_tree$ott_id, sep = '')

phylo$tip.label %in% names_in_tree$ott_id

names_in_tree<- subset(names_in_tree, names_in_tree$ott_id %in% phylo$tip.label)

#which species in the table are in the tree
df$species.updated.rotl<- tolower(df$species.updated.rotl)
df<- subset(df, tolower(df$species.updated.rotl) %in% tolower(names_in_tree$search_string))

#give them the ids in a column sot hat brms can match it up
df$species_id<- names_in_tree$ott_id
```

produce covariance matrix using branch lengths of 1 (as in Fisher et al)
```{r}
# set branch lengths to 1 for covariance matrix
phylo_1b <- compute.brlen(phylo, 1)
#create covariance matrix
CovarMatrix <- ape::vcv.phylo(phylo_1b)

```

define the phylogenetic model
```{r}
#(1|gr(phylo, cov = A))

  get_prior(data = df,
      family=bernoulli(link = 'logit'),
      formula = Obligate_or_facultative ~ 0 + clonal + (1|gr(species_id, cov = CovarMatrix)),
      data2 = list(CovarMatrix = CovarMatrix))

fit_obl_phy<-
  brm(data = df,
      family=bernoulli(link = 'logit'),
      formula = Obligate_or_facultative ~ 0 + clonal + (1|gr(species_id, cov = CovarMatrix)),
      data2 = list(CovarMatrix = CovarMatrix),
      iter = 600000, warmup = 100000, chains = 5, thin = 150, cores = 5,
      prior = c(prior(student_t(3, 0, 20), "sd"),
                prior(normal(0, 10), "b")), file = 'fits/obl_phy')
                


```

Assessing model:
```{r}
plot(fit_obl_phy) #check that chains converged
pp_check(fit_obl_phy) #check the predictions
plot(conditional_effects(fit_obl_phy), points = TRUE) 

summary(fit_obl_phy)
pairs(fit_obl_phy)
posterior_summary(fit_obl_phy, robust = T) #what are the medians for coefficients? if F, then returns means

hyp<- hypothesis(fit_obl_phy,  "clonalclonal > clonalnonMclonal")
plot(hyp)
```

